%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Trim (asktrim.com)} % Organization
    {San Francisco, CA} % Location
    {Nov 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Product and Data:} {Product owner for Trim's savings account. Developing features to improve key metrics for engagement and retention. Designing and implementing A/B tests to measure improvements.}
        \item \textbf{Frontend Engineering:} {Building personal finance management tools, reusable React components, and dashboards to define the Trim UI/UX (D3, React, ReactRedux).}
        \item \textbf{Backend Engineering:} {Implementing frameworks to scalably message the user base, improving transaction categorization and merchant recognition, building a financial product recommendation system based on transaction data (Ruby, Rails, Sidekiq).}
        \item \textbf{Other:} {Conducting hiring interviews across engineering, product, and growth. Providing mentorship to three engineers. Running user interview and research processes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {LiveRamp} % Organization
    {San Francisco, CA} % Location
    {Sep 2016 - Nov 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Frontend Engineering:} {Built client dashboards and internal UIs to manage LiveRamp's CustomerLink product (React, ReactRedux).}
        \item \textbf{Backend Engineering:} {Implemented and maintained internal and external facing RESTful APIs (Ruby, Rails, Swagger).}
        \item \textbf{Hiring:} {Led the engineering organization's participation in improving the diversity of the team, spanning onboarding, conference presence, and university recruiting.}
        \item \textbf{Management:} {Conducted quarterly team feedback sessions, delivering ways to improve team morale and productivity. Managed a 12-week summer intern, providing technical and professional mentorship.}
        \item \textbf{Other:} {Built an internal aliasing system (go/ links) to promote information sharing throughout the company and its parent organization for the company's hackweek.}        
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {iOS Development Intern} % Job title
    {Edify Technologies, Inc.} % Organization
    {Denver, CO} % Location
    {Jun 2015 - Aug 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a broad range of frontend features for a music composition app for kids (Objective-C).}
        \item {Edify was 1 of 10 companies selected out of 600 applicants for Techstars' flagship Boulder program.}
        \item {See my note face animation work at} \textbf{\href{http://www.musiquest.com}{musiquest.com}}.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Instructor} % Job title
    {iD Tech Camps} % Organization
    {Amherst, MA} % Location
    {Jul 2014 - Aug 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught Java programming classes to students aged 7-18.}
        \item {Created lesson plans that catered to the unique learning styles of each student.}
      \end{cvitems}
    }

\end{cventries}
